Concurrent Programming with CXL

### 2020-06-14 book/paper.tex
Latest

>>>>

\chapter{List of CXL Statements}

CXL currently supports the following statements:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{lv = e} & \texttt{lv} is an lvalue and \texttt{e} is an expression\\
\hline
\texttt{pass} & do nothing\\
\hline
\texttt{del lv} & delete\\
\hline
\texttt{call e} & evaluate \texttt{e}\\
\hline
\texttt{assert b [, x]} & \texttt{b} is a Boolean.  If \texttt{False}, optionally print expression \texttt{e}\\
\hline
\texttt{const v = e} & \texttt{v} is an identifier, \texttt{e} is a constant expression\\
\hline
\texttt{def m(v, ...): S} & \texttt{m} and \texttt{v} are identifiers, \texttt{S} a list of statements\\
\hline
\texttt{let v = e, ...: S} & \texttt{e} is an expression, \texttt{S} a list of statements\\
\hline
\texttt{if b: S} & \texttt{b} is a Boolean, \texttt{S} a list of statements\\
\hline
\texttt{while b: S} & \texttt{b} is a Boolean, \texttt{S} a list of statements\\
\hline
\texttt{for v in e: S} & \texttt{e} is a set evaluated in order,
                            \texttt{S} a list of statements\\
\hline
\texttt{atomic: S} & \texttt{S} a list of statements\\
\hline
\texttt{spawn p e [, t]} & \texttt{p} is a method, \texttt{e} is an expression, \texttt{t} is an optional tag (an expression) \\
\hline
\texttt{go c e} & \texttt{c} is a context, \texttt{e} is an expression \\
\hline
\texttt{import m} & \texttt{m} identifies a module \\
\hline
\end{tabular}
\vspace{1em}

To iterate through a dictionary, list, or tuple, use:
\texttt{for v in keys(e):~S}.

\chapter{List of Modules}

The \texttt{bag} module has various useful methods that operate on bags or
multisets:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{bagEmpty()} & returns an empty bag\\
\hline
\texttt{bagFromset(s)} & create a bag from set \texttt{s}\\
\hline
\texttt{bagCount(b, e} & count how many times \texttt{e} occurs in bag \texttt{b}\\
\hline
\texttt{bagChoose(b)} & like \texttt{choose(s)}, but applied to a bag\\
\hline
\texttt{bagAdd(pb, e)} & add one copy of \texttt{e} to bag \texttt{\^{}pb}\\
\hline
\texttt{bagRemove(pb, e)} & remove one copy of \texttt{e} from bag \texttt{\^{}pb}\\
\hline
\end{tabular}
\vspace{1em}

The \texttt{list} module has various useful methods that operate on lists
or tuples:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{subseq(t, b, f)} & return a \emph{slice} of list \texttt{t} starting
at index \texttt{b} and ending just before index \texttt{f}\\
\hline
\texttt{append(t, e)} & append \texttt{e} to list \texttt{t}\\
\hline
\texttt{head(t)} & return the first element of list \texttt{t}\\
\hline
\texttt{tail(t)} & return all but the first element of list \texttt{t}\\
\hline
\texttt{qsort(t)} & sort list \texttt{t} using quicksort\\
\hline
\texttt{sum(t)} & return the sum of all elements in \texttt{t}\\
\hline
\texttt{list2bag(t)} & convert list \texttt{t} into a bag \\
\hline
\end{tabular}
